Figures

### 2020-11-24 manuscript/figures.Rmd
describe figure 2 best fit lines

```{r 01_geometry_base, fig.cap = "Comparison among proxy and true values of lake geometry for A) distance to deepest point versus distance distance to lake center and B) nearshore land slope versus in-lake slope. A best-fit line and coefficient of determination is shown to illustrate representativeness.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_base-1.pdf")
```

>>>>

```{r 01_geometry_base, fig.cap = "Comparison among proxy and true values of lake geometry for A) distance to deepest point versus distance distance to lake center and B) nearshore land slope versus in-lake slope. A best-fit line and equation is shown to shown to facilitate computation of correction factors for proxy values of lake geometry. Coefficients of determination are shown to illustrate representativeness.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_base-1.pdf")
```
